---
title: "Experimental data analysis"
author: "Stine Hansen"
date: "May 14 2018"
output: html_document
---
This script includes the code for fitting a Biased Nash, win-stay/lose-shift and reinforcement learning model on experimental data. The Stan models used can be found here: https://github.com/stineh/bachelor
We include code for checking the posterior predictions (calculating accuracy and plotting this).
The data analysed has the following structure:

ID    trial  Choice     Win
1       1       1       1
1       2       0       1
1       3       1       0
2       1       1       0
2       2       0       1
2       3       0       1


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr); library(ggplot2); library(rstan); library(reshape2)
library(readr); library(tidyverse); library(boot); library(brms)
```

Set WD
```{r}
setwd("") # change to wanted working directory
```

## Biased Nash
Run the model on the data
```{r}
#Import data
MatchingPenniesData <- read_delim("datafile", "\t", escape_double = FALSE, trim_ws = TRUE)

#Change values in data
MatchingPenniesData$S = MatchingPenniesData$S-1
MatchingPenniesData <- transform(MatchingPenniesData,id=as.numeric(factor(subjID)))

#Number of trials and participants
N = 60
P = length(unique(MatchingPenniesData$Subject))

#Retrieve information from the dataset that the Stan model needs
data_real <- list(Subject = MatchingPenniesData$id, y=MatchingPenniesData$S, N=2387, P=P)

#Estimate model on data
nash_fitreal <- stan(file = "nash_real.stan", data = data_real, cores=1, chains=1, iter=1000)
nash_fitreal
```

Calculate accuracy
```{r}
#Retrieve known choices from the data
real_y <- data_frame(variable = MatchingPenniesData$S)

#Retrieve draws from the posterior prediction (from the fit)
postpred_y <- rstan::extract(nash_fitreal, permuted = F, pars = c("y_sim")) %>% # pred. thetas
    plyr::adply(2) %>% 
    dplyr::select(-chains) %>% 
    melt() 

# Create a combined dataframe for plotting the accuracy
names(real_y)[names(real_y)=="variable"] <- "real_value"
real_y$variable = paste('y_sim[',seq.int(nrow(real_y)),']', sep="")
nash_outcome = real_y %>% left_join(postpred_y, by='variable')

#Calculate the accuracy at each trial. There 500 plausible draws for each real_y observation
accuracy = NULL
amount_correct = NULL

for(i in 1:2387) {
  amount_correct[i] = sum(nash_outcome$variable==paste('y_sim[',i,']',sep="") & nash_outcome$real_value==nash_outcome$value)
  accuracy = data.frame(amount_correct)
}

#Calculate percentage
accuracy$percentage = accuracy$amount_correct/500*100

# Get the participant ID and accuracy percentage
accuracy2 = as.data.frame(cbind(accuracy$percentage,MatchingPenniesData$id))
colnames(accuracy2) <- c("percentage","id")

#Calculate the mean accuracy for participants across trials and SE
library(Rmisc)
plot_data = summarySE(accuracy2, "percentage", "id")

# Calculate group mean accuracy
groupAcc <- summarySE(plot_data, "percentage")

#Plot the accuracy for each participant with errorbars displaying SE and the group accuracy
plot <- ggplot(plot_data, aes(percentage, id))
plot + 
  geom_point() +
  geom_errorbarh(aes(xmin=percentage-se, xmax=percentage+se)) +
  ggtitle("Nash fit") +
  ylab("Participant ID") +
  xlab("Accuracy of fit in %")+
  geom_point(data=groupAcc,mapping = aes(x = percentage, y = 0, color="red")) + 
  geom_errorbarh(data=groupAcc, mapping = aes(xmin = percentage-se, xmax=percentage+se,y=0, color="red"))+
  scale_y_continuous(breaks = c(seq(1:40)))
```


## WSLS
Run the model on the data
```{r}
#Retrieve information from the dataset that the Stan model needs
data_realWSLS <- list(subject = MatchingPenniesData$id, right=MatchingPenniesData$S, success=MatchingPenniesData$win, N=2387, P=P)

#Estimate model on data
WSLS_fitreal <- stan(file = "WSLS_real.stan", data = data_realWSLS, cores=1, chains=1, iter=1000)
WSLS_fitreal
```

Calculate accuracy
```{r}
#Retrieve known choices from the data
real_y <- data_frame(variable = MatchingPenniesData$S)

#Retrieve draws from the posterior prediction (from the fit)
postpred_yWSLS <- extract(WSLS_fitreal, permuted = F, pars = c("y_sim")) %>% # 
    plyr::adply(2) %>% 
    dplyr::select(-chains) %>% 
    melt() 

# Create a combined dataframe for plotting the accuracy
names(real_y)[names(real_y)=="variable"] <- "real_value"
real_y$variable = paste('y_sim[',seq.int(nrow(real_y)),']', sep="")
WSLS_outcome = real_y %>% left_join(postpred_yWSLS, by='variable')

#Calculate the accuracy at each trial. There 500 plausible draws for each real_y observation
accuracyWSLS = NULL
amount_correctWSLS = NULL

for(i in 1:2387) {
  amount_correctWSLS[i] = sum(WSLS_outcome$variable==paste('y_sim[',i,']',sep="") & WSLS_outcome$real_value==WSLS_outcome$value)
  accuracyWSLS = data.frame(amount_correctWSLS)
}

#Calculate percentage
accuracyWSLS$percentage = accuracyWSLS$amount_correctWSLS/500*100

# Get the participant ID and accuracy percentage
accuracyWSLS2 = as.data.frame(cbind(accuracyWSLS$percentage,MatchingPenniesData$id))
colnames(accuracyWSLS2) <- c("percentage","id")

#Calculate the mean accuracy for participants across trials and SE
library(Rmisc)
plot_dataWSLS = summarySE(accuracyWSLS2, "percentage", "id")

# Calculate group mean accuracy
groupAccWSLS <- summarySE(WSLSPlotDataReal, "percentage")

#Plot the accuracy for each participant with errorbars displaying SE and the group accuracy
plot <- ggplot(WSLSPlotDataReal, aes(percentage, id))
plot + 
  geom_point() +
  geom_errorbarh(aes(xmin=percentage-se, xmax=percentage+se)) +
  ggtitle("WSLS fit") +
  ylab("Participant ID") +
  xlab("Accuracy of fit in %")+
  geom_point(data=groupAccWSLS,mapping = aes(x = percentage, y = 0, color="red")) + 
  geom_errorbarh(data=groupAccWSLS, mapping = aes(xmin = percentage-se, xmax=percentage+se,y=0, color="red"))+
  scale_y_continuous(breaks = c(seq(1:40)))

```

## Reinforcement learning
Run the model on the data
```{r}
library(hBayesDM)
#Fit data using the hBayesDM package
RL_fitreal <- bandit2arm_delta(data="choose",niter = 1000, nwarmup = 500, nchain = 1, inc_postpred = TRUE)
RL_fitreal
```

Calculate accuracy
```{r}
#Retrieve known choices from the data
real_y <- data.frame(choice = MatchingPenniesData$S, key.participant=MatchingPenniesData$id, key.trial=MatchingPenniesData$t)
# Change trialnumber to run continuously for each participant, makes it easier to combine data later
real_y$trialn <- with(real_y, ave(key.participant, key.participant, FUN = seq_along))

#Retrieve draws from the posterior prediction (from the fit)
postpredRL <- as.data.frame(RL_fitreal$parVals$y_pred)
#from wide to long format
postpredRL <- gather(postpredRL)
postpredRL <- na.omit(postpredRL)

#Split the 'key' column into two seperate columns: trial and participant
library(reshape2)
postpredRL <- transform(rltest2, key = colsplit(key, pattern = "\\.", names = c('participant', 'trial')))

# Rename variables, making joining easier
postpredRL$key.participant <- gsub("X", "", postpredRL$key.participant)

# Create a combined dataframe for plotting the accuracy
library(dplyr)
data <- real_y %>% left_join(postpredRL,by=c("key.participant","trialn"="key.trial"))

#Calculate the accuracy at each trial. There 500 plausible draws for each real_y observation
#Calculate percentage
data2 <- data %>%
  dplyr::mutate(v3 = ifelse(choice==value, 1, 0)) %>%
  group_by(key.participant, trialn) %>% 
  dplyr::summarise(n_v1v2_equal = sum(v3),
                     percentage = n_v1v2_equal / n() * 100)

#Calculate the mean accuracy for participants across trials and SE
plot_dataRL = summarySE(data2, "percentage", "key.participant")

# Calculate group mean accuracy
groupAccRL <- summarySE(plot_dataRL, "percentage")

#Plot the accuracy for each participant with errorbars displaying SE and the group accuracy
plot <- ggplot(plot_dataRL, aes(percentage, key.participant))
plot + 
  geom_point() +
  geom_errorbarh(aes(xmin=percentage-se, xmax=percentage+se)) +
  ggtitle("RL fit") +
  ylab("Participant ID") +
  xlab("Accuracy of fit in %") +
  scale_y_continuous(breaks = c(1:40))+
  geom_point(data=groupAccRL,mapping = aes(x = percentage, y = 0, color="red")) + 
  geom_errorbarh(data=groupAccRL, mapping = aes(xmin = percentage-se, xmax=percentage+se,y=0, color="red"))

```




