---
title: "Data simulation functions and estimating on fake data (model prior checking)"
author: "Stine Hansen"
date: "April 15 2018"
output: html_document
---

This script includes the code for generating datasets for a Biased Nash, win-stay/lose-shift and reinforcement learning model. 
We can then fit models on this simulated data. The Stan models used can be found here: https://github.com/stineh/bachelor
We include code for checking the priors (density plots, known values against estimated, absolute difference)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

pacman::p_load(tidyverse,boot,brms,dplyr,ggplot2,rstan,reshape2,Rmisc)
```

Set WD
```{r}
setwd("") #change to wanted working directory
```

## Simulating datasets
The data simulating functions are made in collaboration with Riccardo Fusaroli.

Set common parameters
```{r}
# Number of participants
P=10
# Trials for each participant (observations)
N=100 #or 1000
```

## Multilevel Optimal Nash w different thetas

```{r}
# Overall log-odds of choosing the right hand
thetaG=0 # logit(0.5) = 0
# Variation by Participant
thetaP=1

#Define function
NashSimulation <- function(Participants, Trials, ThetaGroup,ThetaSubjectVariation){
  
  theta=inv.logit(rnorm(Participants,ThetaGroup,ThetaSubjectVariation)) #create normally distributed theta values, normal distribution

# Setting up the simulation
  # for each trial for each participant, the outcome (0 or 1) is decided by a binomial distribution with probability of success of theta for the participant 
  # returns data frame with outcome, thetaG, thetaP, subjectID
  Outcome=NULL
  for (t in seq(Participants)){
    Outcome_tmp = data.frame(outcome=rbinom(Trials,1,theta[t]),thetaG=inv.logit(ThetaGroup),thetaP=theta[t],subjectID=t)
    if (exists("Outcome")){Outcome=rbind(Outcome,Outcome_tmp)} else {Outcome=Outcome_tmp}
    Outcome_tmp=NULL
  }
  return(Outcome)
}

```


## WSLS
Simulate data for WSLS
```{r}
# Group paramters
StayBiasG=1 
ShiftBiasG=1
BiasVariation=1

#Define function
WSLSsimulationSimple <- function(P,NT,StayBiasG,ShiftBiasG, BiasVariation) {
    # Generating individual parameters for biases
    # normally distributed, mean and variation from group
    StayBias = rep(inv.logit(rnorm(P, StayBiasG, BiasVariation)), each = NT)
    ShiftBias = rep(inv.logit(rnorm(P, ShiftBiasG, BiasVariation)), each = NT)
    
    # Random sequence of successes for the algorithm to adapt
    Success = NA
    for (i in seq(NT * P)) {
      Theta_t = inv.logit(rnorm(1, 0, 1))
      Success[i] = rbinom(1, 1, Theta_t)
    }
    
    # Setting up simulation 
    Outcome = NULL
    Right = NULL

      for (i in seq(NT * P)) {
        # If first trial, then random choice
        if (i == 1) {
          p <- rbinom(1, 1, 0.5)
        }
        # If not first trial, one of these 4 conditions
        else {
          # Choice on previous trial = right hand and Correct
          if (Right[i - 1] == 1 & Success[i - 1] == 1) {
            p = StayBias[i]
          }
          # Choice on previous trial = right hand and inorrect
          else if (Right[i - 1] == 1 & Success[i - 1] == 0) {
            p = 1 - ShiftBias[i]
          } 
          # Choice on previous trial = left hand and inorrect
          else if (Right[i - 1] == 0 & Success[i - 1] == 0) {
            p = ShiftBias[i]
          }
          # Choice on previous trial = left hand and correct
          else if (Right[i - 1] == 0 & Success[i - 1] == 1) {
            p =  1 - StayBias[i]
          }
        }
      
      # Decide choice. Binomially distributed (0 or 1). probability of succes, p decided from nested loop above  
      Right[i] = rbinom(1, 1, p)
      }
    
    # Save to data frame
    Outcome <- data.frame(Right,Success,StayBiasG,StayBias,ShiftBiasG,ShiftBias,Participant = rep(seq(P), each = NT))
    return(Outcome)
}
```

Simulate data for WSLS against WSLS
```{r}
# Define additional paramter for opponent
OtherStayBias=2
OtherShiftBias=2

# Define function 
WSLSsimulationWSLS <- function(P,NT,StayBiasG,ShiftBiasG, BiasVariation,OtherStayBias,OtherShiftBias) {
    
  #Generating individual parameters, also for opponent 
    StayBias = rep(inv.logit(rnorm(P, StayBiasG, BiasVariation)), each = NT)
    ShiftBias = rep(inv.logit(rnorm(P, ShiftBiasG, BiasVariation)), each = NT)
    OtherStayBias=inv.logit(OtherStayBias)
    OtherShiftBias=inv.logit(OtherShiftBias)
    
    # Setting up simulation 
    Success = NULL
    Outcome = NULL
    Right = NULL
    p=NULL
    
    for (i in seq(NT * P)) {
      # If first trial, then random choice for both players
      if (i == 1) {
        p[1] <- rbinom(1, 1, 0.5)
        p[2] <- rbinom(1, 1, 0.5)
      }
      # If not first trial, one of these 4 conditions
      else {
        # Choice on previous trial = right hand and correct
        # For opponent this means a loss, so previous trial = right and incorrect
        if (Right[i - 1] == 1 & Success[i - 1] == 1) {
          p[1] = StayBias[i]
          p[2] = 1 - OtherShiftBias
          
        }
        # Choice on previous trial = right and incorrect
        # For opponent this means a win, so previous choice = left and correct
        else if (Right[i - 1] == 1 & Success[i - 1] == 0) {
          p[1] = 1 - ShiftBias[i]
          p[2] = 1 - OtherStayBias
          
        } 
        # Choice on previous trial = left and incorrect 
        # For opponent this means a win, so previous choice = right and correct
        else if (Right[i - 1] == 0 & Success[i - 1] == 0) {
          p[1] = ShiftBias[i]
          p[2] = OtherStayBias
          
        } 
        # Choice on previous trial = left and correct
        # For opponent this means a loss, so previous choice = left and incorrect
        else if (Right[i - 1] == 0 & Success[i - 1] == 1) {
          p[1] = 1 - StayBias[i]
          p[2] = OtherShiftBias
        }
      }
      
      #Decide choice. Binomially distributed (0 or 1). probability of succes, p decided from nested loop above  
      Right[i] = rbinom(1, 1, p[1])
      OtherChoice=rbinom(1,1, p[2])
      
      # When choosing the same hand as opponent = success 
      if (Right[i] == OtherChoice){
        Success[i]=1
      } else { Success[i]=0}
      
    }
    
    # Save to dataframe 
    Outcome <-
      data.frame(
        Right,
        Success,
        StayBiasG,
        StayBias,
        ShiftBiasG,
        ShiftBias,
        Participant = rep(seq(P), each = NT),
        OtherStayBias,
        OtherShiftBias
      )
    return(Outcome)
}
```

## Reinforcement Learning
Simulate data for RL

```{r}
# Group parameters, log-odds
LearningRateG=0
BiasVariation=1

# Define functions
RLsimulationSimple <- function(P,NT,LearningRateG,BiasVariation,Theta) {
    #Generating individual parameters
    #normally distributed, mean and variation from group 
    LearningRate = rep(inv.logit(rnorm(P, LearningRateG, BiasVariation)), each = NT)
    
    # Random sequence of successes for the algorithm to adapt
    OtherRight = NULL
    for (i in seq(NT * P)) {
      OtherRight[i] = rbinom(1, 1, Theta)
    }
    
    # Setting up simulation
    Outcome = NULL
    Right = NULL
    Success=NULL
    ValueLeft=NULL
    ValueRight=NULL
    
    for (i in seq(NT * P)) {
      # If first trial, then random choice
      # equal values for both hands
      if (i == 1) {
        p <- rbinom(1, 1, 0.5)
        ValueRight[i] = 0.5
        ValueLeft[i] = 0.5
      } 
      # If not first trial, decide if previous trial was left or right hand choice
      else {
        # if previous choice was the right hand
        if (Right[i - 1] == 1) {
          ValueRight[i] = ValueRight[i-1] + LearningRate[i] * (Success[i-1] - ValueRight[i-1])
          ValueLeft[i] = ValueLeft[i-1]
          p = ValueRight[i]
        }
        # if previous choice was the left hand
        else if (Right[i - 1] == 0 ) {
          ValueLeft[i] = ValueLeft[i-1] + LearningRate[i] * (Success[i-1] - ValueLeft[i-1])
          ValueRight[i] = ValueRight[i-1]
          p = 1-ValueLeft[i]
        }
      }
      
      # Decide choice. Probability of success, p is decided above 
      Right[i] = rbinom(1, 1, p)
      # If the choice matches the opponent choice, it is a success
      if (Right[i]==OtherRight[i]){Success[i]=1}else{Success[i]=0}
    }
    # Save to dataframe
    Outcome <- data.frame(Right,Success,ValueRight,ValueLeft,LearningRateG,LearningRate,OtherRight,Participant = rep(seq(P), each = NT))
    return(Outcome)
  }
```

Simulate data for RL against RL
```{r}
# Define parameter for opponent
OtherLearningRate = 1 

#Define function 
RLsimulationRL <- function(P,NT,LearningRateG,BiasVariation,Theta, OtherLearningRate) {
    
    #Generating individual parameters
    LearningRate = rep(inv.logit(rnorm(P, LearningRateG, BiasVariation)), each = NT)
    OtherLearningRate = rep(inv.logit(rnorm(P, OtherLearningRate, BiasVariation)), each = NT)
    
    # Setting up simulation 
    Outcome = NULL
    Right = NULL
    Success=NULL
    ValueLeft=NULL
    ValueRight=NULL
    OtherValueLeft=NULL
    OtherValueRight=NULL
    p=NULL
    
    for (i in seq(NT * P)) {
      # If first trial, then random choice
      if (i == 1) {
        p[1] <- rbinom(1, 1, 0.5)
        ValueRight[i] = 0.5
        ValueLeft[i] = 0.5
        p[2] <- rbinom(1, 1, 0.5)
        OtherValueRight[i] = 0.5
        OtherValueLeft[i] = 0.5
      } 
      else {
        # If not first trial, decide if previous trial was left or right hand choice
        # Previous = Right and correct
        # This means previous = Right and incorrect for opponent
        if (Right[i - 1] == 1) {
          ValueRight[i] = ValueRight[i-1] + LearningRate[i] * (Success[i-1] - ValueRight[i-1])
          ValueLeft[i] = ValueLeft[i-1]
          p[1] = ValueRight[i]
          OtherValueLeft[i] = OtherValueLeft[i-1] + OtherLearningRate[i] * (Success[i-1] - OtherValueLeft[i-1])
          OtherValueRight[i] = OtherValueRight[i-1]
          p[2] = 1-OtherValueLeft[i]
        } 
        
        else if (Right[i - 1] == 0 ) {
          # Previous = Left and incorrect
          # This means previous = left and correct for opponent 
          ValueLeft[i] = ValueLeft[i-1] + LearningRate[i] * (Success[i-1] - ValueLeft[i-1])
          ValueRight[i] = ValueRight[i-1]
          p[1] = 1-ValueLeft[i]
          OtherValueRight[i] = OtherValueRight[i-1] + OtherLearningRate[i] * (Success[i-1] - OtherValueRight[i-1])
          OtherValueLeft[i] = OtherValueLeft[i-1]
          p[2] = OtherValueRight[i]
        }
      }
      
      # Decide choice. Probability of successes, p are decided above
      Right[i] = rbinom(1, 1, p[1])
      OtherRight=rbinom(1,1, p[2])
      
      # If the choice matches the opponent, it is a success
      if (Right[i] == OtherRight) {
        Success[i]=1
      } else { Success[i]=0}
    }
    
    # save to dataframe 
    Outcome <- data.frame(Right,Success,ValueRight,ValueLeft,LearningRateG,LearningRate,OtherRight,Participant = rep(seq(P), each = NT))
    return(Outcome)
}
```

Simulate data for RL vs. WSLS
Combine the two functions 
```{r}
WSLSsimulationRL <- function(P,NT,StayBiasG,ShiftBiasG, BiasVariation,LearningRateG) {
    
  #Generating individual parameters
    StayBias = rep(inv.logit(rnorm(P, StayBiasG, BiasVariation)), each = NT)
    ShiftBias = rep(inv.logit(rnorm(P, ShiftBiasG, BiasVariation)), each = NT)
    LearningRate = rep(inv.logit(rnorm(P, 0, BiasVariation)), each = NT)
    
    # Setting up simulation
    Success = NULL
    Outcome = NULL
    Right = NULL
    p=NULL
    ValueLeft=NULL
    ValueRight=NULL
    
    for (i in seq(NT * P)) {
      # If first trial, then random choice
      if (i == 1) {
        p[1] <- rbinom(1, 1, 0.5)
        p[2] <- rbinom(1, 1, 0.5)
        ValueRight[i] = 0.5
        ValueLeft[i] = 0.5
      } 
      # If not first trial, one of these 4 conditions
      else {
        # Previous = Right 
        # For WSLS opponent: Choice on previous trial = right hand and correct
        if (Right[i - 1] == 1 & Success[i - 1] == 1) {
          p[1] = StayBias[i]
          ValueRight[i] = ValueRight[i-1] + LearningRate[i] * (Success[i-1] - ValueRight[i-1])
          ValueLeft[i] = ValueLeft[i-1]
          p[2] = ValueRight[i]
          
        } 
        # Previous = Right 
        # For WSLS opponent: Choice on previous trial = right and incorrect
        else if (Right[i - 1] == 1 & Success[i - 1] == 0) {
          p[1] = 1 - ShiftBias[i]
          ValueRight[i] = ValueRight[i-1] + LearningRate[i] * (Success[i-1] - ValueRight[i-1])
          ValueLeft[i] = ValueLeft[i-1]
          p[2] = ValueRight[i]
          
        } 
        # Previous = left
        # For WSLS opponent: Choice on previous trial = left and incorrect
        else if (Right[i - 1] == 0 & Success[i - 1] == 0) {
          p[1] = ShiftBias[i]
          ValueLeft[i] = ValueLeft[i-1] + LearningRate[i] * (Success[i-1] - ValueLeft[i-1])
          ValueRight[i] = ValueRight[i-1]
          p[2] = 1-ValueLeft[i]
          
        } 
        # Previous = left
        # For WSLS opponent: Choice on previous trial = left and correct
        else if (Right[i - 1] == 0 & Success[i - 1] == 1) {
          # Previous = Left and Correct; OTHER: Prev = Left and Not Correct
          #print("Stay Left")
          p[1] = 1 - StayBias[i]
          ValueLeft[i] = ValueLeft[i-1] + LearningRate[i] * (Success[i-1] - ValueLeft[i-1])
          ValueRight[i] = ValueRight[i-1]
          p[2] = 1-ValueLeft[i]
        }
      }
      
      # Decide choices
      Right[i] = rbinom(1, 1, p[1])
      OtherChoice=rbinom(1,1, p[2])
      
      # When choices match, it is a success
      if (Right[i] == OtherChoice){
        Success[i]=1
      } else { Success[i]=0}
      
    }
    # Save to dataframe
    Outcome <-
      data.frame(
        Right,
        Success,
        StayBiasG,
        StayBias,
        ShiftBiasG,
        ShiftBias,
        Participant = rep(seq(P), each = NT),
        OtherChoice,
        ValueRight,
        ValueLeft,
        LearningRate
      )
    return(Outcome)
}
```


## Creating datasets
Examples of calling the functions to generate datasets
```{r}
# For Biased Nash
DataNash_G50_P1 <- NashSimulation(P,N,thetaG,thetaP) 
#we can alter the values from the set common ones 
DataNash_G05_P1 <- NashSimulation(P,N,logit(.05),thetaP) 
DataNash_G90_P1 <- NashSimulation(P,N,logit(.9),thetaP)


# For WSLS
DataWSLS_simple_Stay1_Shift1_P1 <- WSLSsimulationSimple(P,N,StayBiasG,ShiftBiasG,BiasVariation)
DataWSLS_simple_Stay0_Shift0_P1 <- WSLSsimulationSimple(P,N,StayBiasG=0,ShiftBiasG=0,BiasVariation)
DataWSLS_simple_Stay2_Shift0_P1 <- WSLSsimulationSimple(P,N,StayBiasG=2,ShiftBiasG=0,BiasVariation)
DataWSLS_simple_Stay0_Shift2_P1 <- WSLSsimulationSimple(P,N,StayBiasG=0,ShiftBiasG=2,BiasVariation)

# For WSLS vs. WSLS
DataWSLS_WSLS_Stay1_Shift1_P1_Ostay2_Oshift2 <- WSLSsimulationWSLS(P,N,StayBiasG,ShiftBiasG, BiasVariation,OtherStayBias,OtherShiftBias) #different biases
DataWSLS_WSLS_Stay1_Shift1_P1_Ostay1_Oshift1 <- WSLSsimulationWSLS(P,N,StayBiasG,ShiftBiasG, BiasVariation,OtherStayBias=1,OtherShiftBias=1) #same biases


# For RL
d1_1 <- RLsimulationSimple(P,N,LearningRateG,BiasVariation,Theta=0.7)
d1_2 <- RLsimulationSimple(P,N,LearningRateG=1,BiasVariation,Theta=0.7)
d1_3 <- RLsimulationSimple(P,N,LearningRateG=2,BiasVariation,Theta=0.7)

d2_1 <- RLsimulationSimple(P,N,LearningRateG,BiasVariation,Theta=0.05)
d2_2 <- RLsimulationSimple(P,N,LearningRateG=1,BiasVariation,Theta=0.05)
d2_3 <- RLsimulationSimple(P,N,LearningRateG=2,BiasVariation,Theta=0.05)
# For RL vs. RL
d3_1 <- RLsimulationRL(P,N,LearningRateG,BiasVariation,Theta=0.7,OtherLearningRate)
d3_2 <- RLsimulationRL(P,N,LearningRateG=1,BiasVariation,Theta=0.7,OtherLearningRate=1)
d3_3 <- RLsimulationRL(P,N,LearningRateG=2,BiasVariation,Theta=0.7,OtherLearningRate=0)

# For RL vs. WSLS
d4_1 <- WSLSsimulationRL(P,N,StayBiasG=1,ShiftBiasG=1,BiasVariation=1, LearningRateG=0)
d4_2 <- WSLSsimulationRL(P,N,StayBiasG=1,ShiftBiasG=1,BiasVariation=1, LearningRateG=1)
```


## Running the Stan models on the generated datasets and plotting
Biased Nash example:
Change the dataframe to run on different dataset
```{r}
# Create list with information to be passed to the Stan model from the data
data_list <- list(Subject = DataNash_G50_P1$subjectID, y=DataNash_G50_P1$outcome, N=N*P, P=P)

# Fit the model on the data
nash_fit <- stan(file = "nash_sim.stan", data = data_list, cores=1, chains=1, iter=1000)
nash_fit

```

Now plot data to assess model estimates against the known values
```{r}
# Retrieve the known parameters from the dataset 
known_parameters <- DataNash_G50_P1 %>% group_by(subjectID) %>% summarise(theta=mean(thetaP))

#Rename the columns and ID variable. Makes combining the data easier later
for (i in seq(P)) {
  known_parameters$subjectID[i] = paste('thetaP[',i,']', sep="")
}
names(known_parameters)[names(known_parameters)=="subjectID"] <- "variable"

#Create a combined dataframe for plotting
#Extract the estimated parameters from the fit
plot_data = extract(nash_fit, permuted = F, pars = c("thetaP")) %>% 
  # Stack chains (wide to long melt), drop the chain label
  plyr::adply(2) %>% 
  dplyr::select(-chains) %>% 
  melt() %>% 
  # Perform a left join with the known parameters
  left_join(known_parameters, by = "variable")

#the estimates are on the logit scale. inverse this to get more intepretable values
plot_data$value = inv.logit(plot_data$value)

#Generate plot
plot_data %>%
  ggplot(aes(x = value)) + 
  geom_density(fill = "cornflowerblue", alpha = 0.5) + # create density plot
  facet_wrap(~ variable, scales = "free") + # display the participants together
  geom_vline(aes(xintercept = (theta)), colour = "red") + # display known value
  ggtitle("Nash thetaG 0.5\nActual parameters and estimates\n") # give title 

#Get the mean and SD for estimated value distributions 
nash50 <- as.data.frame(Rmisc::summarySE(plot_data, "value", c("variable","theta")))
#Calculate absolute difference
nash50$difference <- abs(nash50$theta-nash50$value)
#Save as table in txt format
write.table(nash50, "nash50.txt", sep="\t")

# Print mean difference
summarySE(nash50,"difference")

```


Biased Nash example:
Change the dataframe to run on different dataset
```{r}
# Create list with information to be passed to the Stan model from the data
data_listWSLS <- list(subject = DataWSLS_simple_Stay1_Shift1_P1$Participant, right=DataWSLS_simple_Stay1_Shift1_P1$Right, success = DataWSLS_simple_Stay1_Shift1_P1$Success, N=N*P, P=P)

# Fit the model on the data
WSLS_fit <- stan(file = "WSLS_sim.stan", data = data_listWSLS, cores=3, chains=1, iter=1000)
WSLS_fit
```

Now plot data to assess model estimates against the known values
```{r}
# Retrieve the known parameters from the dataset 
known_parametersWSLS <- DataWSLS_simple_Stay1_Shift1_P1 %>% group_by(Participant) %>% dplyr::summarise(stayBias=mean(StayBias), shiftBias=mean(ShiftBias)) 

#Rename the columns and ID variable. Makes combining the data easier later
for (i in seq(P)) {
  known_parametersWSLS$Participant[i] = paste('stayBiasP[',i,']', sep="")
}
names(known_parametersWSLS)[names(known_parametersWSLS)=="Participant"] <- "variable"

#Create a combined dataframe for plotting the stay bias
#Extract the estimated stay parameters from the fit
plot_dataWSLSStay = extract(WSLS_fit, permuted = F, pars = c("stayBiasP")) %>% 
  # Stack chains, drop the chain label
  plyr::adply(2) %>% 
  dplyr::select(-chains) %>% 
  melt() %>%
  # Perform a left join with the known parameters
  left_join(known_parametersWSLS, by="variable")
# rename variable to make sense
names(plot_dataWSLSStay)[names(plot_dataWSLSStay)=="value"] <- "stayBiasSim"

#Create a combined dataframe for plotting the shift bias
#Extract the estimated shift parameters from the fit
plot_dataWSLSShift = extract(WSLS_fit, permuted = F, pars = c("shiftBiasP")) %>%
  # Stack chains (wide to long melt), drop the chain label
  plyr::adply(2) %>% 
  dplyr::select(-chains) %>% 
  melt()
# rename variable to make sense
names(plot_dataWSLSShift)[names(plot_dataWSLSShift)=="value"] <- "shiftBiasSim"

#Combine stay and shift bias in a single data frame
plot_dataWSLSShift = subset(plot_dataWSLSShift, select=c('shiftBiasSim'))
plot_dataWSLS = cbind(plot_dataWSLSStay, plot_dataWSLSShift)

#the estimates are on the logit scale. inverse this to get more intepretable values
plot_dataWSLS$stayBiasSim = inv.logit(plot_dataWSLS$stayBiasSim)
plot_dataWSLS$shiftBiasSim = inv.logit(plot_dataWSLS$shiftBiasSim)

#Generate plots
stayPlot <- plot_dataWSLS %>%
  ggplot(aes(x = stayBiasSim)) + 
  geom_density(fill = "cornflowerblue", alpha = 0.5) + # create density plot
  facet_wrap(~ variable, scales = "free") + # display the participants together
  geom_vline(aes(xintercept = stayBias), colour = "red") + # display known value
  ggtitle("WSLS stay bias 1, shift bias 1\nActual stay bias and estimates\n") # give title

shiftPlot <- plot_dataWSLS %>%
  ggplot(aes(x = shiftBiasSim)) + 
  geom_density(fill = "cornflowerblue", alpha = 0.5) + # create density plot
  facet_wrap(~ variable, scales = "free") + # display the participants together
  geom_vline(aes(xintercept = shiftBias), colour = "red") + # display known value
  ggtitle("WSLS stay bias 1, shift bias 1\nActual shift bias and estimates\n") # give title


#Get the mean and SD for estimated value distributions 
WSLSstay <- as.data.frame(Rmisc::summarySE(plot_dataWSLS, "stayBiasSim", c("variable","stayBias")))
WSLSshift <- as.data.frame(Rmisc::summarySE(plot_dataWSLS, "shiftBiasSim", c("variable","shiftBias")))

#Calculate absolute difference
WSLSstay$difference <- abs(WSLSstay$stayBias-WSLSstay$stayBiasSim)
WSLSshift$difference <- abs(WSLSshift$shiftBias-WSLSshift$shiftBiasSim)

#Save as table in txt format
write.table(WSLSstay, "WSLSstay.txt", sep="\t")
write.table(WSLSshift, "WSLSshift.txt", sep="\t")

# Print mean difference
summarySE(WSLSstay,"difference")
summarySE(WSLSshift,"difference")

```


Reinforcement learning example:
Change the dataframe to run on different dataset
```{r}
#Load hBayesDM package
library(hBayesDM)

# To use the hBayesDM function bandit2arm_delta, the data has to look a certian way
# Now that we know this, it would be easier to change the data simulation function, but for now we just rename the columns afterwards

#rename ID column
names(d1_1)[names(d1_1)=="Participant"] <- "subjID"
#rename outcome column. Change values from 0 and 1 to 1 and 2
names(d1_1)[names(d1_1)=="Right"] <- "choice"
d1_1$choice = d1_1$choice+1
#rename success. Change values from 0 and 1 to -1 and 1 
names(d1_1)[names(d1_1)=="Success"] <- "outcome"
d1_1$outcome = d1_1$outcome*2-1

#Save this data to a txt file so we can choose it for the bandit2arm_delta function
write.table(d1_1, "simpleRL1.txt", sep="\t")

#Fit model on data
RL_fitSimple1 <- bandit2arm_delta(data =  "choose",niter = 1000, nwarmup = 500, nchain = 1)
RL_fitSimple1
```

Now plot data to assess model estimates against the known values
```{r}
# Retrieve the known parameters from the dataset 
known_parametersRL1 <- d1_1 %>% group_by(subjID) %>% summarise(valueRight=mean(ValueRight), valueLeft=mean(ValueLeft), learningRate=mean(LearningRate))

#Rename the columns and ID variable. Makes combining the data easier later
for (i in seq(P)) {
  known_parametersRL1$subjID[i] = paste('LearningRateP[',i,']', sep="")
}
names(known_parametersRL1)[names(known_parametersRL1)=="subjID"] <- "key"

# Extract estimated learning rate from the fit and save to dataframe
temp = as.data.frame(RL_fitSimple1$parVals$A)
#rename columns to make sense
colnames(temp) <- c("LearningRateP[1]","LearningRateP[2]","LearningRateP[3]","LearningRateP[4]","LearningRateP[5]","LearningRateP[6]","LearningRateP[7]","LearningRateP[8]","LearningRateP[9]","LearningRateP[10]")

#convert data to long format
temp2 = gather(temp)

#create combined data for plotting
plot_dataRLSimple1 = temp2 %>%
  left_join(known_parametersRL1, by="key")

# Generate the plot
plot_dataRLSimple1 %>%
  ggplot(aes(x = value)) + 
  geom_density(fill = "cornflowerblue", alpha = 0.5) +# create density plot
  facet_wrap(~ key, scales = "free") + # display the participants together
  geom_vline(aes(xintercept = learningRate), colour = "red") + # display known value
  ggtitle("RL learning rate of 0\nActual learning rate and estimates\n")# give title

#Get the mean and SD for estimated value distributions 
RL1 <- as.data.frame(Rmisc::summarySE(plot_dataRLSimple1, "value", c("key","learningRate")))

#Calculate absolute difference
RL1$difference <- abs(RL1$value-RL1$learningRate)

#Save as table in txt format
write.table(RL1, "RL1", sep="\t")

# Print mean difference
Rmisc::summarySE(RL1,"difference")

```

